Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint through section 4

In general, checking that $\canonizer(c_2) = \canonizer(c_3)$ is undecidable
because of the {\em normalize} QRE which allows uses an arbitrary
idempotent function as the canonizer. Therefore, our actual implementation of
the composition rule for QRE lenses follows Boomerang's approach, which is to
define the composition on QRE lenses if and only if $c_2$ and $c_3$ are
syntactially equal to $id(R)$ and $id(R')$ for some $R$ and $R'$ satisfying
$\mathcal{L}(R) = \mathcal{L}(R')$.

>>>>

In general, checking that $\canonizer(c_2) = \canonizer(c_3)$ is undecidable
because of the {\em normalize} QRE which allows uses an arbitrary
idempotent function as the canonizer. Therefore, our actual implementation of
the composition rule for QRE lenses follows Boomerang's approach, which is to
define the composition on QRE lenses if and only if $c_2$ and $c_3$ are
syntactially equal to $id(R)$ and $id(R')$ for some $R$ and $R'$ satisfying
$\mathcal{L}(R) = \mathcal{L}(R')$.  \BCP{Here, once again, I worry that we
  are mixing fundamental theory with pragmatic language design /
  implementation, to the detriment of both.  At a theoretical level, this
  restriction is nonsensical, and making it here raises questions like
  ``Does the proof that composition can be normalized away depend on this
  restriction?''}
